---
title: "Analysis"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---
Initialization
===
```{r, message=FALSE}
rm(list=ls())
library(rsurveyutils)
library(lmerTest)
library(here)
library(sjPlot)
library(tidyverse)
library(ggthemr)
library(modelr)
library(tidybayes)
library(emmeans)
# theme_set(theme_bw())
ggthemr("fresh")
library(tidylog)
```


Preprocessing
===

Functions
---
```{r}
```

Read data
---
```{r, message=FALSE}
filepath <- here("data/proc/vbbr_bot_jan2025_indiff.csv")
df_indiff_raw <- read_csv(filepath)
```

```{r}
df_reaps <- read_csv(here("data/proc/vbbr_bot_jan2025_reaps.csv")) %>% 
  rename(
    reap_text = text,
    reap_success = success,
    reap_believable = believable,
    reap_valued = valued,
    reap_relevance = relevance,
    reap_id = id
    ) %>% 
  mutate(
    reap_id = as.numeric(reap_id)
  ) %>% 
  group_by(pid) %>% 
  mutate_at(vars(reap_success, reap_believable, reap_valued, reap_relevance), list(pc=scale)) %>%
  ungroup


# df_reaps %>% 
#   arrange(pid, issue_id, reap_id) %>% view

# read json
val_df <- jsonlite::fromJSON("/Users/ashish/files/research/projects/vbr/precision_reap_bot_react_study/bot/val_list.json") 
val_df %>% pull(name) %>% unique %>% sort
```


Process data
---
```{r, message=FALSE}
df_indiff <- df_indiff_raw %>% 
  filter(use_survey == "Yes") %>% 
  filter(use_survey_beliefs == "Yes, I was paying attention" | is.na(use_survey_beliefs)) %>%
  filter(use_survey_values == "Yes, I was paying attention" | is.na(use_survey_values))

df_vals <- df_indiff %>% 
  select(pid, starts_with("vals_")) %>% 
  pivot_longer(cols = starts_with("vals_"), names_to = "value_name", values_to = "value_rating") %>% 
  mutate(value_name = str_replace_all(value_name, "vals_", "")) %>% 
  mutate(value_name = case_when(
    value_name == "comm" ~ "community",
    value_name == "collab" ~ "collaboration",
    value_name == "selfcontrol" ~ "self_control",
    TRUE ~ value_name
  )) %>% 
  mutate(value_name = case_when(
    str_detect(value_name, "connection") ~ "interpersonalConnection",
    str_detect(value_name, "diversity") ~ "humanDiversity",
    str_detect(value_name, "growth") ~ "personalGrowth",
    str_detect(value_name, "harmony") ~ "interpersonalHarmony",
    str_detect(value_name, "persevere") ~ "perseverance",
    str_detect(value_name, "self_control") ~ "selfControl",
    str_detect(value_name, "environ") ~ "environmentalism",
    TRUE ~ value_name
  )) %>% 
  filter(value_name %in% val_df$name) %>%  # filtering only values in study 2
  group_by(pid) %>%
  mutate(value_rating_pc = scale(value_rating, scale=F)) %>%
  ungroup 
  

df_primals <- df_indiff %>% 
  select(pid, starts_with("primal_")) %>% 
  pivot_longer(cols = starts_with("primal_"), names_to = "primal_name", values_to = "primal_rating") %>% 
  mutate(primal_name = str_replace_all(primal_name, "primal_", "")) %>% 
  mutate(primal_name = case_when(
    primal_name == "needsme" ~ "needs_me",
    primal_name == "worthexploring" ~ "worth_exploring",
    # primal_name == "selfcontrol" ~ "self_control",
    TRUE ~ primal_name
  )) %>% 
  group_by(pid) %>%
  mutate(primal_rating_pc = scale(primal_rating, scale=F)) %>%
  ungroup
# 
# df_vals %>% 
#   mutate(value_name = case_when(
#     str_detect(value_name, "connection") ~ "interpersonalConnection",
#     str_detect(value_name, "diversity") ~ "humanDiversity",
#     str_detect(value_name, "growth") ~ "personalGrowth",
#     str_detect(value_name, "harmony") ~ "interpersonalHarmony",
#     str_detect(value_name, "persevere") ~ "perseverance",
#     str_detect(value_name, "self_control") ~ "selfControl",
#     str_detect(value_name, "environ") ~ "environmentalism",
#     TRUE ~ value_name
#   )) %>% 
#   filter(!value_name %in% val_df$name) %>% 
#   pull(value_name) %>% 
#   unique %>% 
#   sort
```


```{r}
# primals_coding_results_fpath <- here("jupyter/primals_coding_results.csv")
primals_coding_results_fpath <- here("jupyter/df_primals_coding.csv")
df_primals_coding <- read_csv(primals_coding_results_fpath) %>% 
  rename(primal_name = dimension)
  # separate(custom_id, c("pid", "domain", "reap_id", "primal_name"), sep = "-", remove = FALSE) %>% 
  # mutate(code = case_when(
  #   str_detect(tolower(assistant_message), "code\\[0\\]") ~ 0,
  #   str_detect(tolower(assistant_message), "code\\[1\\]") ~ 1,
  #   TRUE ~ NA_real_
  # ))

df_p_code <- df_primals_coding %>% 
  select(pid, domain, primal_name, reap_id, code, assistant_message) 
df_p_code_wide <- df_p_code %>% 
  select(-assistant_message) %>% 
  mutate(primal_name = paste0("primals_", primal_name)) %>%
  pivot_wider(names_from = primal_name, values_from = code) 


# df_p_code %>% 
#   inner_join(df_reaps) %>% 
#   write_csv("~/Downloads/tmplasdkfjalskd.csv")

# Failed lines 1
vals_coding_results_failed_fpath_1 <- here("jupyter/df_other_vals_coding_failed.csv")
df_vals_coding_failed_1 <- read_csv(vals_coding_results_failed_fpath_1) %>% 
  rename(value_name = dimension) %>% 
  mutate(batch_num = as.character(batch_num))
  # separate(custom_id, c("pid", "domain", "reap_id", "value_name"), sep = "-", remove = FALSE) %>% 
  # mutate(code = case_when(
  #   str_detect(tolower(assistant_message), "code\\[0\\]") ~ 0,
  #   str_detect(tolower(assistant_message), "code\\[1\\]") ~ 1,
  #   TRUE ~ NA_real_
  # ))
# Failed lines 3
vals_coding_results_failed_fpath_3 <- here("jupyter/df_other_vals_coding_failed_3.csv")
df_vals_coding_failed_3 <- read_csv(vals_coding_results_failed_fpath_3) %>% 
  rename(value_name = dimension) %>% 
  mutate(batch_num = as.character(batch_num))
  # separate(custom_id, c("pid", "domain", "reap_id", "value_name"), sep = "-", remove = FALSE) %>% 
  # mutate(code = case_when(
  #   str_detect(tolower(assistant_message), "code\\[0\\]") ~ 0,
  #   str_detect(tolower(assistant_message), "code\\[1\\]") ~ 1,
  #   TRUE ~ NA_real_
  # ))

# failed lines 2
vals_coding_results_failed_fpath <- here("jupyter/df_other_vals_coding_failed_2.csv")
df_vals_coding_failed <- read_csv(vals_coding_results_failed_fpath) %>% 
  rename(value_name = dimension) %>% 
  mutate(batch_num = as.character(batch_num)) %>% 
  drop_na(code) %>% 
  bind_rows(df_vals_coding_failed_3) %>% 
  bind_rows(df_vals_coding_failed_1) %>% 
  filter(!duplicated(custom_id))


# vals_coding_results_fpath <- here("jupyter/values_coding_results.csv")
vals_coding_results_fpath <- here("jupyter/df_other_vals_coding.csv")
df_vals_coding <- read_csv(vals_coding_results_fpath) %>% 
  rename(value_name = dimension) %>% 
  filter(!custom_id %in% df_vals_coding_failed$custom_id) %>%
  bind_rows(df_vals_coding_failed) %>% 
  mutate(value_name = case_when(
    str_detect(value_name, "connection") ~ "interpersonalConnection",
    str_detect(value_name, "diversity") ~ "humanDiversity",
    str_detect(value_name, "growth") ~ "personalGrowth",
    str_detect(value_name, "harmony") ~ "interpersonalHarmony",
    str_detect(value_name, "persevere") ~ "perseverance",
    str_detect(value_name, "self_control") ~ "selfControl",
    str_detect(value_name, "environ") ~ "environmentalism",
    TRUE ~ value_name
  )) %>% 
  filter(value_name %in% val_df$name)  # filtering only values in study 2

df_vals_coding %>% 
  group_by(reap_id, value_name) %>% 
  summarize(n = n()) %>% 
  arrange(desc(n)) %>% 
  pull(n) %>%
  table()

df_vals_coding %>%
  group_by(reap_id, value_name) %>% 
  summarize(n = n()) %>% 
  filter(n > 1) 

df_v_code <- df_vals_coding %>% 
  select(pid, domain, value_name, reap_id, code, assistant_message) 
df_v_code_wide <- df_v_code %>% 
  select(-assistant_message) %>% 
  mutate(value_name = paste0("vals_", value_name)) %>%
  pivot_wider(names_from = value_name, values_from = code) 
# count nas in df_v_code_wide
df_v_code_wide %>% 
  select(-pid, -domain, -reap_id) %>% 
  map_dbl(~sum(is.na(.))) %>% 
  sum

```

```{r}
# all_val_names <- df_vals_coding$value_name %>% unique
# d <- expand_grid(reap_id=unique(df_reaps_vals$reap_id), value_name=all_val_names) %>% 
#   left_join(df_reaps_vals)
# 
# d %>% 
#   filter(is.na(value_rating)) %>% 
#   select(reap_id, value_name) %>%
#   write_csv("~/Downloads/tmpasldkfj.csv")
#   
# # ----
# 
# # get failed lines
# df_v_code_wide %>% 
#   pivot_longer(cols = starts_with("vals_"), 
#                names_pattern = "vals_(.*)",
#                names_to = "value_name", 
#                values_to = "code") %>% 
#   filter(is.na(code)) %>% 
#   mutate(value_name = case_when(
#     str_detect(value_name, "interpersonalConnection") ~ "connection",
#     str_detect(value_name, "humanDiversity") ~ "diversity",
#     str_detect(value_name, "personalGrowth") ~ "growth",
#     str_detect(value_name, "interpersonalHarmony") ~ "interpersonal_harmony",
#     TRUE ~ value_name
# 
#   )) %>% #pull(value_name) %>% unique
#   mutate(custom_id = paste0(pid, "-", domain, "-", reap_id, "-", value_name)) %>%
#   write_csv("~/Downloads/tmpsladkfjas.csv")
  
```


```{r}
df_reaps_vals <- df_reaps %>% 
  select(pid,
         domain, 
         reap_id, 
         issue_id,
         reap_text,
         reap_valued, 
         reap_success, 
         reap_relevance, 
         reap_believable, 
         ends_with("_pc")) %>% 
  mutate(reap_id = as.numeric(reap_id)) %>%
  inner_join(df_v_code, by = c("pid", "domain", "reap_id")) %>% 
  inner_join(df_vals) %>% 
  mutate_at(vars(value_rating, 
                 reap_valued,
                 reap_success, 
                 reap_relevance, 
                 ends_with("_pc"),
                 reap_believable) ,
            list(z=scale))

# df_reaps_vals %>% 
#   write_csv("/Users/ashish/files/research/projects/vbr/fine_tuning_vbr/data/raw/value_belief_bot_streamlit/reap_vals.csv")
df_indiff <- df_indiff %>% 
  filter(pid %in% df_reaps$pid)
```


```{r}
df_reaps_beliefs <- df_reaps %>% 
  select(pid, domain, reap_id, reap_text, reap_success, reap_believable, reap_valued, reap_relevance) %>% 
  mutate(reap_id = as.numeric(reap_id)) %>%
  inner_join(df_p_code, by = c("pid", "domain", "reap_id")) %>% 
  inner_join(df_primals) %>% 
  filter(!primal_name %in% c("good", "safe", "enticing", "alive")) %>% 
  mutate_at(vars(primal_rating_pc, reap_success, reap_believable, reap_valued, reap_relevance), list(z=scale)) 
```


```{r}
df_issues_file <- read_csv(here("data/raw/sql_export/issues.csv"))

df_issues <- df_issues_file %>% 
  rename(pid = participant_id) %>% 
  filter(pid %in% df_reaps$pid) %>% 
  rename(issue_id = id)
```

```{r}
df_issues %>% 
  select(pid, issue_id, summary) %>% 
  inner_join(df_reaps_vals) %>% 
  # inner_join(df_reaps %>% 
  #              select(pid, issue_id, reap_id, reap_text)) %>%
  # inner_join(df_vals %>% 
  #              select(pid, value_name) %>% 
  #              filter(value_name %in% df_reaps_vals$value_name)) %>% 
  writexl::write_xlsx(here("data/proc/vbbr_bot_jan2025_reaps_issues_EMMA_coding.xlsx"))
```

```{r}
# df_uncertainty_raw <- read_csv(here("jupyter/uncertainty_coding_results.csv"))
# df_uncertainty <- df_uncertainty_raw %>% 
#   rowwise %>% 
#   mutate(rating = mean(c(rating_1, rating_2, rating_3), na.rm=T)) %>% 
#   ungroup
```

zoib
---
```{r}
library(brms)
zi_coi_zoib <- 
  custom_family("zi_coi_zoib", 
                dpars = c("mu", "zi", "coi", "phi"),
                links = c("logit", "logit", "logit", "log"),
                lb = c(0, 0, 0, 0),
                ub = c(1, 1, 1, NA),
                type = "real")
stan_funs <- "
  real zi_coi_zoib_lpdf(real y, real mu, real zi, real coi, real phi) { 
    row_vector[2] shape = [mu * phi, (1 - mu) * phi];
  
    if (y == 0) { 
      return log(zi); 
    } else if (y == 1) {
      return log1m(zi) + log(coi);
    } else {
      return beta_lpdf(y | shape[1], shape[2]) + log1m(zi) + log1m(coi);
    }
  }
"
stanvars <- stanvar(scode = stan_funs, block = "functions")


posterior_predict_zi_coi_zoib <- function(i, prep, ...) {
  mu <- brms::get_dpar(prep, "mu", i = i)
  zi <- brms::get_dpar(prep, "zi", i = i)
  coi <- brms::get_dpar(prep, "coi", i = i)
  phi <- brms::get_dpar(prep, "phi", i = i)
  
  shape1 <- mu * phi
  shape2 <- (1 - mu) * phi
  
  # Generate uniform random variables
  u <- runif(prep$ndraws)
  
  # Compute cumulative probabilities
  cdf_zero <- zi
  cdf_one <- zi + (1 - zi) * coi
  
  # Initialize output vector
  y <- numeric(prep$ndraws)
  
  # Assign outcomes based on cumulative probabilities
  y[u < cdf_zero] <- 0
  y[u >= cdf_zero & u < cdf_one] <- 1
  
  # For the remaining cases, draw from the beta distribution
  beta_indices <- which(u >= cdf_one)
  y[beta_indices] <- rbeta(length(beta_indices), shape1, shape2)
  
  return(y)
}

posterior_epred_zi_coi_zoib <- function(prep) {
  # Extract distributional parameters from 'prep'
  mu <- brms::get_dpar(prep, "mu")
  zi <- brms::get_dpar(prep, "zi")    # Zero-inflation probability
  coi <- brms::get_dpar(prep, "coi")  # Conditional one-inflation probability
  
  # Calculate the expected value E[Y]
  EY <- (1 - zi) * (coi + (1 - coi) * mu)
  
  return(EY)
}
```

Export coding sheet
===
```{r}
set.seed(123)
df_reaps_vals %>% 
  select(pid, domain, reap_id, issue_id, reap_text, value_name) %>%
  left_join(df_issues %>% select(pid, issue_id, summary), 
            by=c("pid", "issue_id")) %>%
  sample_n(200) %>% 
  writexl::write_xlsx(here("data/proc/vbbr_bot_jan2025_reaps_vals_blind_coding.xlsx"))
  
```


Import blind coding
===
```{r}
df_coding_suze <- readxl::read_xlsx(here("data/vbbr_bot_jan2025_reaps_vals_blind_coding_SUZE_20250219.xlsx")) %>% 
  rename(suze_code = Code) 
df_coding_emma <- readxl::read_xlsx(here("data/vbbr_bot_jan2025_reaps_vals_blind_coding_EMMA_20250219.xlsx"))
```


```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```


```{r}
df_indiff %>% 
  filter(pid %in% df_reaps_vals$pid) %>% 
  count(gender) %>% 
  mutate(pr = (n*100)/sum(n)) %>% 
  as.data.frame

df_indiff %>% 
  summarize(
    mean_age = mean(age),
    sd_age = sd(age, na.rm=T),
    min_age = min(age),
    max_age = max(age)
  ) %>% 
  as.data.frame

df_indiff %>% 
  select(matches("race_[0-9]+$")) %>% 
  pivot_longer(everything()) %>% 
  drop_na(value) %>% 
  count(value) %>% 
  mutate(pr = (n*100)/nrow(df_indiff)) %>% 
  as.data.frame
```

Coding agreement
===
```{r}
library(psych)
d <- df_coding_suze %>% 
  left_join(df_reaps_vals %>% 
              select(pid, reap_id, value_name, code) %>% 
              rename(gpt_code = code)) %>% 
  select(suze_code, gpt_code) %>% 
  as.data.frame

cohen.kappa(d)

sum(d$suze_code == d$gpt_code) / nrow(d)
```

```{r}

d <- df_coding_emma %>% 
  left_join(df_reaps_vals %>% 
              select(pid, reap_id, value_name, code) %>% 
              rename(gpt_code = code)) %>% 
  select(emma_code, gpt_code) %>% 
  as.data.frame

cohen.kappa(d)

sum(d$emma_code == d$gpt_code, na.rm=T) / nrow(d)
```

```{r}
d <- df_coding_emma %>% 
  left_join(df_coding_suze) %>% 
  select(emma_code, suze_code) %>% 
  as.data.frame

cohen.kappa(d)

sum(d$suze_code == d$emma_code, na.rm = T) / nrow(d)
```





Frequencies of beliefs
===
```{r}

df_reaps_beliefs %>% 
  group_by(primal_name) %>% 
  count(code) %>% 
  mutate(pr = n/sum(n)) %>%
  mutate(code = paste0("code_", code)) %>%
  pivot_wider(names_from = code, values_from = c(n, pr)) %>% 
  arrange(n_code_1, .desc=T) %>% 
  view
  
```


Frequencies of values
===
```{r}
df_reaps_vals %>% 
  group_by(value_name) %>% 
  count(code) %>% 
  mutate(pr = n/sum(n)) %>%
  mutate(code = paste0("code_", code)) %>%
  pivot_wider(names_from = code, values_from = c(n, pr)) %>% 
  arrange(n_code_1, .desc=T) %>% 
  view

```

Efficacy of values
===
```{r}
df_reaps_vals %>% 
  filter(code == 1) %>%
  group_by(value_name) %>% 
  summarize(
    mean_success = mean(reap_success),
    sd_success = sd(reap_success),
    mean_relevance = mean(reap_relevance),
    mean_believable = mean(reap_believable),
    mean_valued = mean(reap_valued),
    n = n()
  ) %>% 
  arrange(mean_valued, .desc=T) %>% 
  view
```




Distributions
===

Primals
---
```{r}
df_primals %>% 
  ggplot(aes(x = primal_rating)) +
  geom_histogram(bins=20) + 
  facet_wrap(~primal_name)
```


Bot enjoy
---
```{r}
df_indiff %>% 
  ggplot(aes(x = bot_enjoy)) +
  geom_histogram()
mean(df_indiff$bot_enjoy)
median(df_indiff$bot_enjoy)
sd(df_indiff$bot_enjoy)
```

Bot reuse
---
```{r}
df_indiff %>% 
  ggplot(aes(x = bot_reuse)) +
  geom_histogram()
mean(df_indiff$bot_reuse)
median(df_indiff$bot_reuse)
sd(df_indiff$bot_reuse)
```

Bot helpful
---
```{r}
df_indiff %>% 
  ggplot(aes(x = bot_helpful)) +
  geom_histogram()
mean(df_indiff$bot_helpful)
median(df_indiff$bot_helpful)
sd(df_indiff$bot_helpful)
```

Reap variables
---
```{r}
mean(df_reaps$reap_success == 0)
mean(df_reaps$reap_relevance == 0)
mean(df_reaps$reap_believable == 0)
mean(df_reaps$reap_valued == 0)
mean(df_reaps$reap_success < 5)
df_reaps$reap_success %>% hist
df_reaps$reap_relevance %>% hist
df_reaps$reap_believable %>% hist
df_reaps$reap_valued %>% hist
```

Bot experience and primals
===

enjoy - improvable
```{r}
fit <- lm(bot_enjoy ~ primal_improvable, data=df_indiff)
tab_model(fit)
plot_model(fit, type="slope")
```

helpful - improvable
```{r}
fit <- lm(bot_helpful ~ primal_improvable, data=df_indiff)
tab_model(fit)
plot_model(fit, type="slope")
```

reuse - improvable
```{r}
fit <- lm(bot_reuse ~ primal_improvable, data=df_indiff)
tab_model(fit)
plot_model(fit, type="slope")

```

```{r}
df_reaps_beliefs %>% 
  group_by(primal_name) %>% 
  count(code) %>%
  mutate(pr = n/sum(n)) %>%
  view
```


Outcome correlation
===
```{r}
fit <- df_reaps %>% 
  lmer(reap_success ~ reap_believable + (1|pid) + (1|domain), data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


Values and success
===
```{r}
fit <- df_reaps_vals %>% 
  lmer(reap_success_z ~ value_rating_pc_z * code 
       + (1 | pid) 
       # + (1 | value_name) 
       # + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")


fit <- df_reaps_vals %>% 
  # mutate_at(vars(reap_success, value_rating_pc), ~./100) %>%
  filter(code == 1) %>% 
  lmer(reap_success ~ value_rating_pc
       + (1 | pid) 
       # + (value_rating_pc | value_name)
       # + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="slope")
```

```{r}
d <- df_reaps_vals %>%
  filter(code == 1) %>%
  mutate(reap_success = reap_success/100) %>% 
  mutate(value_rating_pc = value_rating_pc/100)
f <- bf(reap_success ~ value_rating_pc + (1|pid),
        # sigma ~ value_rating_pc + (1|pid)
        )
fit <- brm(f, 
           data=d, 
           chains=4, 
           cores=4, 
           iter=5000, 
           file = "models/success_linear.rds",
           file_refit = "on_change",
           warmup=1000)
summary(fit)

                
epreds <- d %>% 
  data_grid(value_rating_pc = seq_range(value_rating_pc, n = 200)) %>%
  add_epred_draws(fit, re_formula = NA) 

epreds %>%
  ggplot(aes(x = value_rating_pc, y = .epred)) +
  # stat_halfeye(position = position_dodge(0), scale=.2) + 
  # stat_summary(aes(group = 1), geom="line") + 
  stat_lineribbon() +
  scale_fill_brewer() +
  theme_bw()
ggsave("plots/asem_congruence_success.png", width = 8, height = 6)



                
epreds <- d %>% 
  data_grid(value_rating_pc = seq_range(value_rating_pc, n = 200)) %>%
  add_epred_draws(fit, re_formula = NA) 
epreds %>% 
  group_by(reap_category) %>%
  summarize(
    mean = mean(.epred)
  ) %>% 
  as.data.frame


```


```{r}
d <- df_reaps_vals %>% 
  filter(code == 1) %>% 
  left_join(df_indiff %>% 
              select(pid, gender)) %>% 
  filter(gender %in% c("Male", "Female"))
fit <- lmer(reap_success_z ~ value_rating_pc_z * gender + 
       + (1 | pid) 
       # + (1 | value_name) 
       # + (1 | domain)
       , data=d)
tab_model(fit)
plot_model(fit, type="int")
```

zoib
---
```{r}
d <- df_reaps_vals %>%
  mutate(reap_success = reap_success/100)
f <- bf(reap_success ~ value_rating_pc_z * code + (1|pid), 
        zi ~ value_rating_pc_z * code + (1|pid),
        coi ~ value_rating_pc_z * code + (1|pid),
        phi ~ value_rating_pc_z * code + (1|pid)
)
fit_success_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # backend = "cmdstanr",
           algorithm = "meanfield",
           control = list(adapt_delta = .85),
           file = "models/success_zoib.rds",
           # file_refit = "on_change")
           file_refit = "always")
summary(fit_success_zoib)
pp_check(fit_success_zoib)
```

zoib no interaction
---
```{r}
d <- df_reaps_vals %>%
  filter(code == 1) %>%
  mutate(reap_success = reap_success/100)
mean(d$reap_success > .95)
mean(d$reap_success == 1)
mean(d$reap_success == 0)
mean(d$reap_success < .05)
f <- bf(reap_success ~ value_rating_pc_z + (1|pid), 
        zi ~ value_rating_pc_z + (1|pid),
        coi ~ value_rating_pc_z + (1|pid),
        phi ~ value_rating_pc_z + (1|pid)
)
fit_success_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           backend = "cmdstanr",
           control = list(adapt_delta = .9),
           file = "models/success_zoib_noInt.rds",
           file_refit = "on_change")
           # file_refit = "always")
summary(fit_success_zoib)
pp_check(fit_success_zoib)

```



giving or getting mentorship - same for leadership
clarify in second reframing
put two reframings before questions about reframigns - counter balance

thinking about issue from this perspective

for address waht you care about add aassuming it's factually true
add use survyes

Values and valued
===
```{r}
fit <- df_reaps_vals %>% 
  # lmer(reap_valued_pc_z ~ value_rating_pc_z * code
  lmer(reap_valued_z ~ value_rating_pc_z * code
       + (1 | pid) 
       + (1 | value_name) 
       + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")


fit <- df_reaps_vals %>% 
  filter(code == 1) %>% 
  # lmer(reap_valued_pc_z ~ value_rating_pc_z
  lmer(reap_valued_z ~ value_rating_pc_z
       + (value_rating_pc_z | pid) 
       # + (1 | value_name) 
       # + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

zoib
---
```{r}
d <- df_reaps_vals %>%
  mutate(reap_valued = reap_valued/100)

f <- bf(reap_valued ~ value_rating_pc_z * code + (1|pid), 
        zi ~ value_rating_pc_z * code + (1|pid),
        coi ~ value_rating_pc_z * code + (1|pid),
        phi ~ value_rating_pc_z * code + (1|pid)
)

fit_valued_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # control = list(adapt_delta = .85),
           file = "models/valued_zoib.rds",
           # file_refit = "on_change")
           file_refit = "always")
summary(fit_valued_zoib)
pp_check(fit_valued_zoib)
```


zoib no interaction
---
```{r}

d <- df_reaps_vals %>%
  filter(code == 1) %>% 
  mutate(reap_valued = reap_valued/100)

f <- bf(reap_valued ~ value_rating_pc_z + (1|pid), 
        zi ~ value_rating_pc_z + (1|pid),
        coi ~ value_rating_pc_z + (1|pid),
        phi ~ value_rating_pc_z + (1|pid)
)

fit_valued_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # control = list(adapt_delta = .85),
           file = "models/valued_zoib_noInt.rds",
           file_refit = "on_change")
           # file_refit = "always")
summary(fit_valued_zoib)
pp_check(fit_valued_zoib)
```


Values and believability
===
```{r}
fit <- df_reaps_vals %>% 
  lmer(reap_believable_z ~ value_rating_pc_z * code + (1 |pid) + (1 |value_name) + (1|domain), data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

zoib
---
```{r}
d <- df_reaps_vals %>%
  mutate(reap_believable = reap_believable/100)

f <- bf(reap_believable ~ value_rating_pc_z * code + (1|pid), 
        zi ~ value_rating_pc_z * code + (1|pid),
        coi ~ value_rating_pc_z * code + (1|pid),
        phi ~ value_rating_pc_z * code + (1|pid)
)

fit_believable_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # control = list(adapt_delta = .85),
           file = "models/believable_zoib.rds",
           # file_refit = "on_change")
           file_refit = "always")

summary(fit_believable_zoib)
pp_check(fit_believable_zoib)

```



Values and relevance
===
```{r}
d <- df_reaps_vals %>%
  mutate(reap_relevance = reap_relevance/100) %>% 
  mutate(value_rating_pc = value_rating_pc/100)
f <- bf(reap_relevance ~ value_rating_pc + (1|pid))
fit <- brm(f, 
           data=d, 
           chains=4, 
           cores=4, 
           iter=5000, 
           file = "models/relevance_linear.rds",
           warmup=1000)
summary(fit)

```


```{r}
hist(df_reaps_vals$reap_relevance)
mean(df_reaps_vals$reap_relevance == 1)
mean(df_reaps_vals$reap_relevance > 95)
mean(df_reaps_vals$reap_relevance == 0)
fit <- df_reaps_vals %>% 
  lmer(reap_relevance ~ value_rating_pc * code 
       + (1 | pid) 
       + (1 | value_name) 
       + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

```{r}
fit <- df_reaps_vals %>% 
  filter(code == 1) %>% 
  lmer(reap_relevance_z ~ value_rating_pc_z +
       + (1 | pid) 
       # + (1 | value_name) 
       # + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


```{r}
fit <- df_reaps_vals %>% 
  mutate(reap_relevance = reap_relevance/100) %>% 
  filter(code == 1) %>%
  lmer(reap_relevance ~ value_rating_pc
       + (1 | pid) 
       + (1 | value_name) 
       + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


```{r}

fit <- df_reaps_vals %>% 
  lmer(reap_relevance_z ~ value_rating_pc_z * code 
       + (1 | pid) 
       + (1 | value_name) 
       + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

```{r}

fit <- df_reaps_vals %>% 
  filter(code == 1) %>%
  lmer(reap_relevance_z ~ value_rating_pc_z 
       + (value_rating_pc_z | pid) 
       + (value_rating_pc_z | value_name) 
       + (value_rating_pc_z | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


zoib
---
```{r}
d <- df_reaps_vals %>%
  mutate(reap_relevance = reap_relevance/100)

f <- bf(reap_relevance ~ value_rating_pc_z * code + (1|pid), 
        zi ~ value_rating_pc_z * code + (1|pid),
        coi ~ value_rating_pc_z * code + (1|pid),
        phi ~ value_rating_pc_z * code + (1|pid)
)

fit_relevance_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # control = list(adapt_delta = .85),
           file = "models/relevance_zoib.rds",
           # file_refit = "on_change")
           file_refit = "always")

summary(fit_relevance_zoib)
pp_check(fit_relevance_zoib)
```

```{r}

f <- bf(reap_relevance ~ 1 + (1|pid), 
        zi ~ 1 + (1|pid),
        coi ~ 1 + (1|pid),
        phi ~ 1 + (1|pid)
)
fit_relevance_intercept_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # prior = priors,
           # control = list(adapt_delta = .95, max_treedepth = 15),
           file = "models/relevance_zoib_intercept.rds",
           file_refit = "on_change")
           # file_refit = "always")
```

zoib no interaction
---
```{r}
d <- df_reaps_vals %>% 
  filter(code == 1) %>%
  mutate(reap_relevance = reap_relevance/100)


f <- bf(reap_relevance ~ 1 + (1|pid), 
        zi ~ value_rating_pc_z + (1|pid),
        coi ~ value_rating_pc_z + (1|pid),
        phi ~ 1 + (1|pid)
)
priors <- c(
  # Fixed effects (slopes)
  prior(normal(0, 1), class = "b"),
  prior(normal(0, 1), class = "b", dpar = "zi"),
  prior(normal(0, 1), class = "b", dpar = "coi"),
  prior(normal(0, 1), class = "b", dpar = "phi"),

  # Random effect standard deviations (regularizing priors)
  prior(exponential(2), class = "sd"),  # For main model
  prior(exponential(2), class = "sd", dpar = "zi"),  # Zero-inflation
  prior(exponential(2), class = "sd", dpar = "coi"), # One-inflation
  prior(exponential(2), class = "sd", dpar = "phi")  # Dispersion
)
# fit <- brm(f,
#            data = d,
#            family = zi_coi_zoib,
#            chains = 4,
#            cores = 4,
#            iter = 5000,
#            warmup = 2000,
#            stanvars = stanvars,
#            prior = priors,
#            sample_prior = "only",
# )
# pp_check(fit)
# summary(fit)
fit_relevance_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           backend = "cmdstanr",
           # prior = priors,
           # control = list(adapt_delta = .95, max_treedepth = 15),
           file = "models/relevance_zoib_noInt.rds",
           file_refit = "on_change")
           # file_refit = "always")

summary(fit_relevance_zoib)
pp_check(fit_relevance_zoib)
```

```{r}

```


zoib no interaction no ranef
---
```{r}
d <- df_reaps_vals %>% 
  filter(code == 1) %>%
  mutate(reap_relevance = reap_relevance/100)


f <- bf(reap_relevance ~ value_rating_pc_z, 
        zi ~ value_rating_pc_z,
        coi ~ value_rating_pc_z,
        phi ~ value_rating_pc_z
)
# priors <- c(
#   prior(normal(0, 1), class = "b"),          
#   prior(normal(0, 1), class = "b", dpar = "zi"),  
#   prior(normal(0, 1), class = "b", dpar = "coi"),
#   prior(normal(0, 1), class = "b", dpar = "phi")
# )
# fit <- brm(f,
#            data = d,
#            family = zi_coi_zoib,
#            chains = 4,
#            cores = 4,
#            iter = 5000,
#            warmup = 2000,
#            stanvars = stanvars,
#            prior = priors,
#            sample_prior = "only",
# )
# pp_check(fit)
# summary(fit)
fit_relevance_zoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           # prior = priors,
           # control = list(adapt_delta = .95, max_treedepth = 15),
           file = "models/relevance_zoib_noInt.rds",
           file_refit = "on_change")
           # file_refit = "always")

summary(fit_relevance_zoib)
pp_check(fit_relevance_zoib)
```

Do llms pick up on values and put the right values in
===
gonna do a logistic regression to see if value rating predicts the probability of whether a value will be included or not
```{r}

fit <- df_reaps_vals %>% 
  mutate(value_rating_pc = value_rating_pc/100) %>%
  glmer(code ~ value_rating_pc 
        + (value_rating_pc|pid) 
        + (value_rating_pc|value_name), 
        family=binomial, 
        data=.)
summary(fit)
tab_model(fit)

# fit <- df_reaps_vals %>% 
#   mutate(value_rating_pc = value_rating_pc/100) %>%
#   glmer(code ~ value_rating_pc 
#         + (1|pid) 
#         + (1|value_name), 
#         family=binomial, 
#         data=.)
# summary(fit)
# tab_model(fit)
```

```{r}

fit <- df_reaps_vals %>% 
  group_by(pid, domain, issue_id, value_name) %>% 
  summarize(
    value_rating_pc = mean(value_rating_pc),
    code = max(code)
  ) %>% 
  ungroup %>% 
  mutate(value_rating_pc = value_rating_pc/100) %>%
  glmer(code ~ value_rating_pc 
        + (value_rating_pc|pid) 
        + (value_rating_pc|value_name), 
        family=binomial, 
        data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="pred")
ggsave("~/Downloads/tmp_plot.png", width=8, height=6)
```

shuffled
```{r}


shuffled_values_mod <- function(){
  df_pids <- df_reaps_vals %>% 
    dplyr::select(pid) %>% 
    dplyr::filter(!duplicated(pid)) %>% 
    dplyr::mutate(pid_map = sample(pid))

  d <- df_reaps_vals %>% 
    dplyr::select(-value_rating_pc) %>%
    dplyr::group_by(pid, domain, issue_id, value_name) %>% 
    dplyr::summarize(
      code = max(code)
    ) %>% 
    dplyr::ungroup() %>% 
    dplyr::left_join(df_pids) %>% 
    dplyr::select(-pid) %>% 
    dplyr::rename(pid = pid_map) %>% 
    dplyr::left_join(df_vals %>% 
                select(pid, value_name, value_rating_pc)) %>%
    dplyr::mutate(value_rating_pc = value_rating_pc/100)
  
  fit <- d %>%
    glmer(code ~ value_rating_pc 
          + (value_rating_pc|pid) 
          + (value_rating_pc|value_name), 
          family=binomial, 
          data=.)
  return(broom.mixed::tidy(fit))
}

mods <- map(1:500, ~shuffled_values_mod())

# save to disk
# saveRDS(mods, "models/shuffled_values_mods.rds")
mods <- readRDS("models/shuffled_values_mods.rds") 

bind_rows(mods, .id="iter") %>% 
  mutate(iter = as.numeric(iter)) %>% 
  group_by(term) %>% 
  summarize(
    mean = mean(estimate),
    or = mean(exp(estimate)),
    hdi_low = HDInterval::hdi(exp(estimate), credMass = .95)[["lower"]],
    hdi_hi = HDInterval::hdi(exp(estimate), credMass = .95)[["upper"]],
    sd = sd(estimate)
  ) %>% 
  ungroup() 

HDInterval::hdi(c(1, 2, 3, 4, 5), credMass = .95)[["lower"]]
```





Beliefs and success
===
```{r}
fit <- df_reaps_beliefs %>% 
  lmer(reap_success_z ~ primal_rating_pc_z * code 
       + (1|pid) 
       + (1|primal_name)
       + (1|domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


```{r}

d <- df_reaps_beliefs %>%
  mutate(reap_success = reap_success/100)
f <- bf(reap_success ~ primal_rating_pc * code + (1|primal_name))
# f <- bf(reap_success ~ primal_rating_pc * code + (1|pid) + (1|primal_name) + (1|domain))
fit_success_customZoib <- brm(f,
           data = d,
           family = zi_coi_zoib,
           chains = 4,
           cores = 4,
           iter = 5000,
           warmup = 1000,
           stanvars = stanvars,
           control = list(adapt_delta = .85),
           file = "models/success_customZoib.rds",
           file_refit = "on_change")
           # file_refit = "always")
summary(fit)
```

Primal present only rows
---
```{r}
fit <- df_reaps_beliefs %>% 
  filter(code == 1) %>%
  lmer(reap_success ~ primal_rating_pc + (1|pid) + (primal_rating_pc|primal_name) + (1|domain), data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

Individual primals
---
```{r}
df_mods <- df_reaps_beliefs %>% 
  group_by(primal_name) %>% 
  nest() %>%
  mutate(fit = map(data, ~lmer(reap_success ~ primal_rating_pc * code + (1|pid) + (1|domain), data=.))) %>%
  mutate(params = map(fit, broom.mixed::tidy)) %>% 
  select(-data) %>% 
  unnest(params) 

df_mods %>% 
  filter(term == "primal_rating_pc:code") %>% 
  view
```

Domain specific
---
```{r}
fit <- df_reaps_beliefs %>% 
  filter(domain == "career") %>% 
  lmer(reap_success_z ~ primal_rating_pc_z * code 
       + (1|pid) 
       + (1|primal_name)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
fit <- df_reaps_beliefs %>% 
  filter(domain == "relationship") %>% 
  lmer(reap_success_z ~ primal_rating_pc_z * code 
       + (1|pid) 
       + (1|primal_name)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

logistic
---
```{r}

fit <- df_reaps_beliefs %>% 
  mutate(reap_success = if_else(reap_success > 0, 1, 0)) %>%
  glmer(reap_success ~ primal_rating_pc_z * code 
       + (1|pid) 
       + (1|domain)
       + (1|primal_name),
       family = binomial,
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```


Beliefs and believability
===

```{r}
fit <- df_reaps_beliefs %>% 
  lmer(reap_believable_z ~ primal_rating_pc_z * code + (1|pid) + (1|primal_name) + (1|domain), data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

Beliefs and valued
===
```{r}
fit <- df_reaps_beliefs %>% 
  lmer(reap_valued_z ~ primal_rating_pc_z * code + (1|pid) + (1|primal_name) + (1|domain), data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")

```

Beliefs and relevance
===
```{r}
fit <- df_reaps_beliefs %>% 
  lmer(reap_relevance_z ~ primal_rating_pc_z * code 
       + (1 | pid) 
       + (1 | primal_name) 
       + (1 | domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

predict success based on all other vars
===
```{r}
d <- df_reaps_beliefs %>%
  group_by(pid) %>%
  mutate_at(vars(reap_success, reap_believable, reap_valued, reap_relevance), list(pc = ~scale(., scale=F, center=T))) %>%
  ungroup() %>%
  mutate_at(vars(ends_with("_pc"), reap_success), list(z = ~scale(., scale=T))) 
fit <- d %>% 
  lmer(reap_success_z ~ reap_believable_pc_z + reap_valued_pc_z + reap_relevance_pc_z 
       + (1 | pid) 
       + (1 | primal_name) 
       + (1 | domain)
       , data=.)
tab_model(fit)
```

Uncertainty moderator of belief congruence
===
```{r}
d <- df_reaps_beliefs %>% 
  left_join(df_uncertainty %>% 
              select(pid, domain, rating))

fit <- d %>% 
  lmer(reap_success_z ~ primal_rating_pc_z * code * rating
       + (1|pid) 
       + (1|primal_name)
       + (1|domain)
       , data=.)
summary(fit)
tab_model(fit)
plot_model(fit, type="int")
```

Session Info
===
```{r}
sessionInfo()
```

```{r}
df = readxl::read_excel("~/Downloads/VBR_congruence_20240609_sample.xlsx")
df %>% 
  mutate(row = row_number() + 1) %>% 
  filter(!is.na(code_binary)) %>% 
  mutate(agree = code_binary == gpt_code_binary) %>% 
  filter(!agree) %>% 
  view
```




