---
title: "Preprocessing script"
author: "Ashish"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    theme: paper
---

Initialization
===
```{r, message=FALSE}
rm(list=ls())
# devtools::install_github("amehtaSF/rsurveyutils")
library(rsurveyutils)
library(qualtRics)
library(here)
library(tidyverse)
library(tidylog)
library(lubridate)
library(lubridate)
theme_set(theme_bw())
```

```{r}
clean_names <- function(df) {
  df %>%
    rename_with(~ .x %>%
                  str_replace_all("StartDate", "start_date") %>% # Replace "StartDate" with "start_date
                  str_replace_all("EndDate", "end_date") %>%     # Replace "EndDate" with "end_date"
                  str_replace_all("RecordedDate", "recorded_date") %>% # Replace "RecordedDate" with "recorded_date"
                  str_replace_all("IPAddress", "ip_address") %>% 
                  tolower() %>%                  # Convert to lowercase
                  str_replace_all("[^[:alnum:]]", "_") %>% # Replace non-alphanumeric with "_"
                  str_replace_all("_+", "_") %>% # Replace multiple "_" with a single "_"
                  str_remove_all("^_|_$")        # Remove leading/trailing "_"
    )
}
```


Preprocessing
===

Gather data
---
```{r}
# gather_script_fpath <- here("rscripts/gather.sh")
# system(paste("source ~/.bash_profile && bash", gather_script_fpath))
```

a

Read data
---
```{r}
filepath <- sprintf("%s/vbbr_bot_jan2025.csv", recent_date_dir(here("data/raw")))
df_file_round1 <- read_survey(here(filepath))

filepath <- sprintf("%s/vbbr_bot_jan2025_postbot.csv", recent_date_dir(here("data/raw")))
df_file_postbot <- read_survey(here(filepath)) %>% 
  mutate(STUDY_ID = "677db0064cdaa4ae7dd475b8-postbot")

filepath <- sprintf("%s/vbbr_bot_jan2025_round2.csv", recent_date_dir(here("data/raw")))
df_file_round2 <- read_survey(here(filepath))

df_file <- df_file_round1 %>% 
  bind_rows(df_file_postbot) %>% 
  bind_rows(df_file_round2) %>% 
  clean_names()

STUDY_ID_PILOT <- "6779b83c25f35fc959988dfc"
STUDY_ID_R1 <- "677db0064cdaa4ae7dd475b8"
STUDY_ID_R1_FIX <- "677db0064cdaa4ae7dd475b8-postbot"
STUDY_ID_R2 <- "677df225125f646cc31fdd75"
STUDY_ID_R3 <- "677e2778cd69193846bccea3"


# df_file %>%
#   names %>%
#   cat(sep = "\n")
df_file %>% 
  filter(prolific_id == "66ba08ae50bac2bbfa96393c")
```


Read codebooks
---
```{r}

codebook_filepath <- "data/vbbr_bot_codebook.xlsx"

codebook_vars <- readxl::read_excel(here(codebook_filepath), sheet="rename")
codebook_values <- readxl::read_excel(here(codebook_filepath), sheet="recode")
```

Process data
---
```{r}
df_raw <- df_file %>% 
  # -- remove qualtrics erroneous header -- #
  # slice(-1) %>% 
  # -- add raw data file name -- #
  mutate(rawDataFile = filepath) %>% 
  # -- drop columns with all NA -- #
  select(-where(~all(is.na(.)))) %>% 
  # -- rename columns -- #
  codebook_renamer(names_from=codebook_vars$old_var_name,
                   names_to=codebook_vars$new_var_name) 
                   names_to=codebook_vars$new_var_name) 
```

```{r}
df_recoded <- df_raw %>% 
  # -- recode variables -- #
  codebook_recoder(var_regex=codebook_values$var_name,
                   values_from=codebook_values$old_val,
                   values_to=codebook_values$new_val)
```


```{r}

pids_w_qualtrics_fix <- df_recoded %>% 
  filter(study_id == STUDY_ID_R1_FIX) %>% 
  pull(prolific_id)

df_proc_0 <- df_recoded %>% 
  # -- remove columns with all NA -- #
  select_if(~!all(is.na(.))) %>% 
  # -- rename pid -- #
  rename(pid = prolific_id) %>% 
  mutate(pid = str_remove_all(pid, " ")) %>%
  # -- convert dates to datetime -- #
  mutate(
    start_date = ymd_hms(start_date),
    end_date = ymd_hms(end_date),
    recorded_date = ymd_hms(recorded_date)
  ) %>% 
  # -- select study version -- #
  filter(study_id != STUDY_ID_PILOT) %>%
  # filter(study_id == STUDY_ID_PILOT) %>%
  # filter(study_id == STUDY_ID_R1) %>%
  # filter(study_id == STUDY_ID_R1_FIX) %>%
  # filter(study_id == STUDY_ID_R2) %>%
  # filter(study_id == STUDY_ID_R3) %>%
  
  
  # -- filter incompletes -- #
  # filter(!is.na(use_survey)) %>% 
  # -- arrange by date -- #
  arrange(start_date)

# Dealing with the fact I had to give some participants a separate link for the second half of their survey
df_proc_fixed_pt1 <- df_proc_0 %>% 
  filter(pid %in% pids_w_qualtrics_fix) %>% 
  filter(study_id == STUDY_ID_R1) %>% 
  select(-(bot_enjoy:rawDataFile), pid)

df_proc_fixed_pt1 %>% 
  filter(duplicated(pid))

df_proc_fixed_pt2 <- df_proc_0 %>% 
  filter(pid %in% pids_w_qualtrics_fix) %>% 
  filter(study_id == STUDY_ID_R1_FIX) %>% 
  select(pid, bot_enjoy:rawDataFile) %>% 
  filter(!duplicated(pid))

df_proc_fixed_pt2 %>% 
  filter(pid %in% 
           (df_proc_fixed_pt2 %>% 
              filter(duplicated(pid)) %>% 
              pull(pid))
         ) %>% 
  view

df_proc <- df_proc_0 %>% 
  filter(!pid %in% pids_w_qualtrics_fix) %>% 
  bind_rows(
    df_proc_fixed_pt1 %>% 
      inner_join(df_proc_fixed_pt2, by="pid"))

  


# -- Check for duplicates -- #
df_proc %>% 
  group_by(pid) %>% 
  summarize(n = n()) %>%
  arrange(desc(n)) 
```


```{r}
source("secrets.R")  # load api_key
check_ip <- function(ip_address, api_key) {  
  require(jsonlite)
  require(httr)  
  # Construct the URL  
  url <- paste0("https://vpnapi.io/api/", ip_address, "?key=", api_key)    
  # Send the API request  
  response <- httr::GET(url)    
  # Check if the request was successful  
  if (httr::http_status(response)$category == "Success") {    
    # Parse the JSON response    
    parsed_response <- jsonlite::fromJSON(httr::content(response, "text", encoding = "UTF-8"))
    # Extract desired fields into a named list    
    extracted_data <- list(      
      IP_country = parsed_response$location$country,      
      IP_vpn = parsed_response$security$vpn,      
      IP_tor = parsed_response$security$tor,      
      IP_proxy = parsed_response$security$proxy,      
      IP_relay = parsed_response$security$relay    
    )        
    # Return the output as a dataframe    
    return(as.data.frame(extracted_data))  
  } else {    
    # If request was not successful, print error message    
    cat("Error:", httr::http_status(response)$reason, "\n")    
    return(NULL)  
  }}

# df_ipChecked <- df_proc %>%
#   # filter(study_id == STUDY_ID_R3) %>% 
#   select(pid, ip_address) %>%
#   mutate(ip_info = map(ip_address, ~check_ip(.x, api_key))) %>%
#   unnest(ip_info)
# df_ipChecked %>%
#   filter(IP_vpn == TRUE | IP_tor == TRUE | IP_proxy == TRUE | IP_relay == TRUE)

# 
# pids_vpn <- df_ipChecked %>% 
#   filter(IP_vpn == TRUE | IP_tor == TRUE | IP_proxy == TRUE | IP_relay == TRUE) %>% 
#   pull(pid)
# df_file %>% 
#   filter(prolific_id %in% pids_vpn) %>% 
#   view
# 
# df_messages %>% 
#   filter(pid == "5dee8ee31255595293a9906b") %>% 
#   view
# 
# df_messages %>% 
#   filter(pid == "671d309dd87b3db020d02f1a") %>% 
#   view
# 
# df_participants %>% 
#   filter(pid == "671d309dd87b3db020d02f1a") %>% 
#   view
# 
# df_proc %>% 
#   filter(pid == "671d309dd87b3db020d02f1a") %>% 
#   select(contains("ac")) %>% 
#   view

```

Check AC
---
```{r}
d_fail <- df_proc %>% 
  mutate_at(vars(ac_vals, ac_vals_2), as.numeric) %>% 
  filter(ac_vals != 99 | 
           (ac_vals_2 > 27 | ac_vals_2 < 23) | # 25
           ac_primals != "Strongly disagree")

d_fail %>% 
  select(pid, ac_vals, ac_vals_2, ac_primals) 
failed_ac_pids <- d_fail$pid

d_fail$ac_vals
d_fail$ac_vals_2
d_fail$ac_primals
```



Read chatbot data
---

DEAL WITH PIDs with 2nd attempt
5f1db15b22c07d01e51960ad-2 
65e1204f1bee2811d7894471-2


```{r}
filepath_participants <- here("data/raw/sql_export/participants.csv")
df_participants_file <- read_csv(filepath_participants) %>% 
  rename(pid = id)
  rename(pid = id)

filepath_messages <- here("data/raw/sql_export/messages.csv")
df_messages_file <- read_csv(filepath_messages) %>% 
  rename(pid = participant_id)
  rename(pid = participant_id)

filepath_issues <- here("data/raw/sql_export/issues.csv")
df_issues_file <- read_csv(filepath_issues) %>% 
  rename(pid = participant_id)
  rename(pid = participant_id)

filepath_reappraisals <- here("data/raw/sql_export/reappraisals.csv")
df_reaps_file <- read_csv(filepath_reappraisals)  %>% 
  rename(pid = participant_id)

pids_w_2nd_attempt <- df_participants_file %>% 
  filter(str_detect(pid, "-2$")) %>% 
  mutate(pid = str_remove(pid, "-2")) %>%
  pull(pid)


```

Process chatbot data
---
```{r}

qualtrics_join_keep_cols <- c("pid", "feedback_txt", "use_survey", "study_id")

df_participants <- df_participants_file %>% 
  # -- remove tests -- # 
  filter(!str_detect(pid, "^test")) %>% 
  filter(!str_detect(pid, "^99999")) %>% 
  filter(!str_detect(pid, "^11111")) %>% 
  filter(!str_detect(pid, "^22222")) %>% 
  filter(!str_detect(pid, "^00000")) %>% 
  # -- fix malformed pid -- #
  mutate(pid = str_replace_all(pid, " directly into.*", "")) %>% 
  # -- fix 2nd attempt pids -- #
  filter(!pid %in% pids_w_2nd_attempt) %>%
  mutate(pid = str_remove(pid, "-2$")) %>% 
  # -- keep only responses with qualtrics -- #
  inner_join(df_proc %>% 
               select(one_of(qualtrics_join_keep_cols))) %>% 
  # -- remove attention check fails -- #
  filter(!pid %in% failed_ac_pids) %>% 
  # -- remove incomplete chat interactions -- #
  filter(cur_state == "end")

df_messages <- df_messages_file %>% 
  # -- fix 2nd attempt pids -- #
  filter(!pid %in% pids_w_2nd_attempt) %>%
  mutate(pid = str_remove(pid, "-2$"))  %>% 
  # -- keep only responses with qualtrics -- #
  inner_join(df_proc %>% 
               select(pid, feedback_txt, use_survey)) %>% 
  # -- keep only responses in df_participants (ie completed chatbot) -- #
  filter(pid %in% df_participants$pid) %>%
  # -- remove attention check fails -- #
  filter(!pid %in% failed_ac_pids)

df_issues <- df_issues_file %>% 
  # -- fix 2nd attempt pids -- #
  filter(!pid %in% pids_w_2nd_attempt) %>%
  mutate(pid = str_remove(pid, "-2$"))  %>% 
  # -- keep only responses with qualtrics -- #
  inner_join(df_proc %>% 
               select(one_of(qualtrics_join_keep_cols))) %>% 
  # -- keep only responses in df_participants (ie completed chatbot) -- #
  filter(pid %in% df_participants$pid) %>%
  # -- remove attention check fails -- #
  filter(!pid %in% failed_ac_pids)


df_reaps <- df_reaps_file %>% 
  # -- fix 2nd attempt pids -- #
  filter(!pid %in% pids_w_2nd_attempt) %>%
  mutate(pid = str_remove(pid, "-2$"))  %>% 
  # -- keep only responses with qualtrics -- #
  inner_join(df_proc %>% 
               select(one_of(qualtrics_join_keep_cols))) %>% 
  # -- keep only responses in df_participants (ie completed chatbot) -- #
  filter(pid %in% df_participants$pid) %>%
  # -- remove attention check fails -- #
  filter(!pid %in% failed_ac_pids)

```


individual differences
===

```{r}
# 
# subscales_items <- list(
#   primal_abundant = c('primal_ab1', 'primal_ab2x', 'primal_ab3', 'primal_ab4'),
#   primal_harmless = c('primal_ht1x', 'primal_ht2', 'primal_ht3', 'primal_ht4x', 'primal_ht5'),
#   primal_hierarchical = c('primal_hn1', 'primal_hn2', 'primal_hn3', 'primal_hn4x', 'primal_hn5'),
#   primal_improvable = c('primal_it1', 'primal_it2', 'primal_it3', 'primal_it4x', 'primal_it5'),
#   primal_intentional = c('primal_iu1', 'primal_iu2', 'primal_iu3x', 'primal_iu4x', 'primal_iu5'),
#   primal_interactive = c('primal_ii1', 'primal_ii2', 'primal_ii3', 'primal_ii4x', 'primal_ii5'),
#   primal_interesting = c('primal_ib1x', 'primal_ib2x', 'primal_ib3x', 'primal_ib4'),
#   primal_just = c('primal_ju1', 'primal_ju2x', 'primal_ju3', 'primal_ju4', 'primal_ju5'),
#   primal_regenerative = c('primal_rd1x', 'primal_rd2', 'primal_rd3', 'primal_rd4x')
# )
#  
# # Compute alphas for each subscale
# alphas <- map_dfr(names(subscales_items), function(scale_name) {
#   items <- subscales_items[[scale_name]]
#   # Select the relevant items from df_proc
#   df_items <- df_recoded %>% select(all_of(items))
#   # Compute Cronbach's alpha
#   alpha_value <- psych::alpha(df_items)$total$std.alpha
#   # Return a dataframe with the subscale name and alpha value
#   tibble(scale = scale_name, alpha = alpha_value)
# })

df_proc %>% 
  select(starts_with("primal_ab")) %>% 
  psych::alpha()
df_proc %>% 
  select(starts_with("primal_au")) %>% 
  psych::alpha()

df_proc %>% 
  select(starts_with("primal_ht")) %>% 
  psych::alpha()

df_indiff <- df_proc %>% 
  filter(use_survey == "Yes") %>%
  filter(!pid %in% failed_ac_pids) %>%
  filter(pid %in% df_participants$pid) %>% 
   mutate(
    primal_abundant = (primal_ab1 + primal_ab2x + primal_ab3 + primal_ab4) / 4,
    primal_acceptable = (primal_au1x + primal_au2x + primal_au3x + primal_au4) / 4,
    primal_beautiful = (primal_bu1x + primal_bu2 + primal_bu3 + primal_bu4) / 4,
    primal_changing = (primal_cs1 + primal_cs2 + primal_cs3 + primal_cs4x + primal_cs5) / 5,
    primal_cooperative = (primal_cc1x + primal_cc2x + primal_cc3x + primal_cc4) / 4,
    primal_funny = (primal_fh1 + primal_fh2 + primal_fh3x + primal_fh4) / 4,
    primal_harmless = (primal_ht1x + primal_ht2 + primal_ht3 + primal_ht4x + primal_ht5) / 5,
    primal_hierarchical = (primal_hn1 + primal_hn2 + primal_hn3 + primal_hn4x + primal_hn5) / 5,
    primal_improvable = (primal_it1 + primal_it2 + primal_it3 + primal_it4x + primal_it5) / 5,
    primal_intentional = (primal_iu1 + primal_iu2 + primal_iu3x + primal_iu4x + primal_iu5) / 5,
    primal_interactive = (primal_ii1 + primal_ii2 + primal_ii3 + primal_ii4x + primal_ii5) / 5,
    primal_interconnected = (primal_ia1 + primal_ia2 + primal_ia3 + primal_ia4x) / 4,
    primal_interesting = (primal_ib1x + primal_ib2x + primal_ib3x + primal_ib4) / 4,
    primal_just = (primal_ju1 + primal_ju2x + primal_ju3 + primal_ju4 + primal_ju5) / 5,
    primal_meaningful = (primal_mm1x + primal_mm2x + primal_mm3x + primal_mm4) / 4,
    primal_needsme = (primal_nd1 + primal_nd2 + primal_nd3 + primal_nd4x) / 4,
    primal_pleasurable = (primal_pm1x + primal_pm2x + primal_pm3 + primal_pm4 + primal_pm5) / 5,
    primal_progressing = (primal_pd1x + primal_pd2x + primal_pd3 + primal_pd4) / 4,
    primal_regenerative = (primal_rd1x + primal_rd2 + primal_rd3 + primal_rd4x) / 4,
    primal_stable = (primal_sf1x + primal_sf2x + primal_sf3x + primal_sf4) / 4,
    primal_understandable = (primal_ut1 + primal_ut2 + primal_ut3x + primal_ut4x) / 4,
    primal_worthexploring = (primal_wn1 + primal_wn2 + primal_wn3 + primal_wn4x) / 4,
    primal_safe = (primal_cc1x + primal_cc2x + primal_cc3x + primal_cc4 + primal_ht1x + 
                     primal_ht2 + primal_ht3 + primal_ht4x + primal_ht5 + primal_ju2x + 
                     primal_ju4 + primal_ju5 + primal_pm1x + primal_pm2x + primal_pm3 + 
                     primal_pm4 + primal_pm5 + primal_pd1x + primal_pd2x + primal_pd3 + 
                     primal_pd4 + primal_rd1x + primal_rd2 + primal_rd3 + primal_rd4x + 
                     primal_sf1x + primal_sf2x + primal_sf3x + primal_sf4) / 29,
    primal_enticing = (primal_ab1 + primal_ab2x + primal_ab3 + primal_ab4 + primal_bu1x + 
                         primal_bu2 + primal_bu3 + primal_bu4 + primal_fh1 + primal_fh2 + 
                         primal_fh3x + primal_fh4 + primal_it2 + primal_it3 + primal_it5 + 
                         primal_ib1x + primal_ib2x + primal_ib3x + primal_ib4 + primal_mm1x + 
                         primal_mm2x + primal_mm3x + primal_mm4 + primal_wn1 + primal_wn2 + 
                         primal_wn3 + primal_wn4x + primal_e1 + primal_e2) / 28,
    primal_alive = (primal_iu1 + primal_iu2 + primal_iu3x + primal_iu4x + primal_iu5 + 
                      primal_ii1 + primal_ii3 + primal_ii4x + primal_ii5 + primal_ju3 + 
                      primal_nd1 + primal_nd2 + primal_nd3 + primal_nd4x) / 14,
    primal_good = (primal_ab1 + primal_ab2x + primal_ab3 + primal_ab4 + primal_bu1x + 
                     primal_bu2 + primal_bu3 + primal_bu4 + primal_cc1x + primal_cc2x + 
                     primal_cc3x + primal_cc4 + primal_fh1 + primal_fh2 + primal_fh3x + 
                     primal_fh4 + primal_ht1x + primal_ht2 + primal_ht3 + primal_ht4x + 
                     primal_ht5 + primal_it1 + primal_it2 + primal_it3 + primal_it4x + 
                     primal_it5 + primal_ib1x + primal_ib2x + primal_ib3x + primal_ib4 + 
                     primal_ju1 + primal_ju2x + primal_ju3 + primal_ju4 + primal_ju5 + 
                     primal_mm1x + primal_mm2x + primal_mm3x + primal_mm4 + primal_nd1 + 
                     primal_nd2 + primal_nd3 + primal_nd4x + primal_pm1x + primal_pm2x + 
                     primal_pm3 + primal_pm4 + primal_pm5 + primal_pd1x + primal_pd2x + 
                     primal_pd3 + primal_pd4 + primal_rd1x + primal_rd2 + primal_rd3 + 
                     primal_rd4x + primal_sf1x + primal_sf2x + primal_sf3x + primal_sf4 + 
                     primal_ut1 + primal_ut2 + primal_ut3x + primal_ut4x + primal_wn1 + 
                     primal_wn2 + primal_wn3 + primal_wn4x + primal_g1x + primal_e1 + 
                     primal_e2) / 71
  ) %>% 
  tally_scale("twivi_conformity") %>% 
  tally_scale("twivi_tradition") %>% 
  tally_scale("twivi_hedonism") %>%
  tally_scale("twivi_stimulation") %>%
  tally_scale("twivi_selfdirection") %>%
  tally_scale("twivi_benevolence") %>%
  tally_scale("twivi_universalism") %>%
  tally_scale("twivi_power") %>%
  tally_scale("twivi_achievement") %>%
  tally_scale("twivi_security") %>% 
  select(pid, start_date, end_date, 
         bot_enjoy, bot_helpful, bot_reuse,
         matches("primal_[a-z]+$"),
         matches("twivi_[a-z]+$"),
         starts_with("vals_"),
         age, starts_with("gender"), starts_with("race"), 
         income, edu,
         use_survey,  use_survey_values, use_survey_beliefs,
         q240, q246, feedback_txt, study_id, rawDataFile) 
```



Approvals
===

easy approval
```{r}
approved_pids <- df_participants %>% 
  filter(cur_state == "end") %>% 
  inner_join(df_proc %>% 
               filter(study_id == STUDY_ID_R2) %>%
               filter(!pid %in% failed_ac_pids) %>%
               filter(use_survey == "Yes")) %>% 
  pull(pid) 
approved_pids %>%
  cat(sep="\n")

df_messages %>% 
  filter(pid %in% approved_pids) %>% 
  filter(tolower(role) == "user") %>% 
  arrange(pid, created_at) %>%
  write_csv("~/Downloads/approved_messages.csv")
```

main approval
---
```{r}

tmp_pids <- read_csv("~/Downloads/prolific_export_677db0064cdaa4ae7dd475b8.csv") %>% 
  filter(Status == "AWAITING REVIEW") %>% 
  pull(`Participant id`)
df_participants %>% 
  filter(study_id == STUDY_ID_R1_FIX) %>% 
  filter(pid %in% tmp_pids) %>%
  pull(pid) %>% 
  unique %>% 
  cat(sep="\n")
```


check individual participants
```{r}

id_to_check = "66ba08ae50bac2bbfa96393c"

df_participants_file %>% 
  filter(pid == id_to_check) %>% 
  view


df_proc %>% 
  select(pid, ac_vals, ac_vals_2, ac_primals, bot_enjoy, bot_helpful, bot_reuse, q240, feedback_txt) %>%
  filter(pid == id_to_check) %>% 
  view



df_file %>% 
  select(prolific_id, ac_vals_1_1, ac_vals_2_1, ac_primals, bot_enjoy_1, bot_helpful_1, q243_1, q240,q246, feedback_txt) %>%
  filter(prolific_id == id_to_check) %>% 
  view


df_messages_file %>% 
  filter(pid == id_to_check) %>% 
  view

df_messages_file %>% 
  filter(pid == id_to_check) %>% 
  view

df_reaps %>% 
  filter(pid == id_to_check) %>% 
  view


df_proc %>% 
  filter(pid == id_to_check) %>% 
  select(contains("ac")) %>% view




df_proc %>% 
  filter(pid == id_to_check) %>% 
  select(contains("ac")) %>% view



```



```{r}
df_messages_file %>% 
  group_by(prolific_id) %>% 
  summarize(n = n()) %>% 
  view
```

Get incompletes
```{r}
completed_chatbot_ids <- df_participants %>% 
  filter(cur_state == "end") %>% 
  pull(pid)
df_proc %>% 
  filter(!pid %in% completed_chatbot_ids) %>% 
  pull(pid)
```



Get people who finished chatbot, but never turned in survey
```{r}
# df_participants %>% 
#   filter(cur_state == "end") %>% 
#   filter(!pid %in% failed_ac_pids) %>% 
#   filter(!pid %in% approved_pids) %>% 
#   select(pid) %>% 
#   write_csv("~/Downloads/tmp.csv")




```

```{r, echo=FALSE}
# ------ End Preprocessing ------ #
# ----- Run all chunks above -----#
```


bad ids
5fc6f4cff3df11159190cbef
65b3cfc2f4ff8a59dd149013
663e3ff81f442e7ad943a761
65e379fd46ad361e29cd00aa
65b3cfc2f4ff8a59dd149013
6696d3feb3d6e70378ecceca

Export
===
```{r}
# filepath_output <- paste0("data/proc/", Sys.Date(), "/_proc.csv")
filepath_output <- paste0("data/proc/vbbr_bot_jan2025_proc.csv")
df_proc %>% 
  write_csv(here(filepath_output))

df_indiff %>% 
  write_csv(here("data/proc/vbbr_bot_jan2025_indiff.csv"))

df_participants %>% 
  write_csv(here("data/proc/vbbr_bot_jan2025_participants.csv"))

df_messages %>%
  write_csv(here("data/proc/vbbr_bot_jan2025_messages.csv"))

df_issues %>%
  write_csv(here("data/proc/vbbr_bot_jan2025_issues.csv"))

df_reaps %>%
  write_csv(here("data/proc/vbbr_bot_jan2025_reaps.csv"))
```




Session Info
===
```{r}
sessionInfo()
```

